Practical Machine Learning Project 1
========================================================

Weight Lifting Exercises Dataset Analysis

By analysising weight lifting exercises, the movements of the belt, arm, and dumbbell can help classifying different activities. Selected features for training the model are as the following:
Belt:
roll_belt, pitch_belt, yaw_belt, total_accel_belt
Arm:
roll_arm, pitch_arm, yaw_arm, total_accel_arm,
Dumbbell:
roll_dumbbell, pitch_dumbbell, yaw_dumbbell, total_accel_dumbbell

this project utilizes Caret library to train data model and to do predictions.

```{r}
library(caret)
```

Read source files:
```{r}
trainData <- read.csv(file="pml-training.csv")
testData <- read.csv(file="pml-testing.csv")
```

to Create subset of raw data source for trainging and prediction

```{r}
trainSet<-trainData[, c("roll_belt","pitch_belt","yaw_belt",
                        "total_accel_belt","roll_arm","pitch_arm",
                        "yaw_arm","total_accel_arm","roll_dumbbell",
                        "pitch_dumbbell","yaw_dumbbell",
                        "total_accel_dumbbell","classe")]

testSet<-testData[, c("roll_belt","pitch_belt","yaw_belt",
                      "total_accel_belt","roll_arm","pitch_arm",
                      "yaw_arm","total_accel_arm","roll_dumbbell",
                      "pitch_dumbbell","yaw_dumbbell",
                      "total_accel_dumbbell","problem_id")]
```

Partition raw training data source to create cross-validation dataset.

```{r}
inTrain<-createDataPartition(y=trainSet$classe,p=0.8,list=FALSE)
cvSet<-trainSet[-inTrain,]
trainSet<-trainSet[inTrain,]
```

Using Naive Bayes to train data model:
```{r eval=FALSE}
model<-train(classe ~ .,data=trainSet,method = "nb")
```

Applying model to cross-validation set to estimate prediction error:

```{r eval=FALSE}
prdtCV<-predict(model,cvSet)
table(prdtCV, cvSet$classe)
```

prdtCV   A   B   C   D   E <br>
     A  805 191 215 155  92 <br>
     B  121 419  64  87 102 <br>
     C  80  72 326  94  43 <br>
     D  108  60  62 292  94 <br>
     E   2  17  17  15 390 <br>

Result comparasion revealed that there's 57% chance the model would give correct prediction.

Applying model to test dataset:

```{r eval=FALSE}
prdtTst<-predict(model,testSet)
prdtTst
```



